{\it E}nKCF: Ensemble of Kernelized Correlation Filters for High-Speed Object Tracking

### 2017-12-02 wacv_for_review.tex
Last Stretch comments added
last.

The KCF solves essentially the problem of a regression in the form of
the regularization (ridge regression):
\begin{equation}
E(h) = \frac{1}{2}||\mathbf{y}-\sum_{c=1}^{C}\mathbf{h_{c}}*\mathbf{x_{c}}||^{2} + \frac{\lambda}{2}\sum_{c=1}^{C}||\mathbf{h_{c}}||^{2}
\label{eq:Closedform_RidgeReg}
\end{equation}
where we seek for $\mathbf{h}$ that minimizes $E$ given the desired
continuous response, $\mathbf{y}$, and the training template
$\mathbf{x}$.  The parameter $c$ enables one to integrate features in
the form of multiple channels, such as HoG and color, in this setup
\cite{henriques2015high,galoogahi2013multi}.  A closed-form solution
for Equation \ref{eq:Closedform_RidgeReg} exists. To simplify the
closed-form solution, an element-wise multiplication in frequency
domain was proposed to learn the frequency domain correspondence of
$\mathbf{h}$, $\mathbf{\hat{w}}$:
\begin{equation}
\mathbf{\hat{w}} = \mathbf{\hat{x}^{*}}*\mathbf{\hat{y}}(\mathbf{\hat{x}^{*}}*\mathbf{\hat{x}}+\lambda)^{-1}.
\label{eq:DiagonalizedPrimalSolution}
\end{equation}
A non-linear version of $\mathbf{\hat{w}}$, $\mathbf{\hat{\alpha}}$ , is proposed to increase robustness
to any geometric and photometric variations
\cite{henriques2015high}. In particular, the diagonalized non-linear Fourier
domain dual form solution is expressed as
\begin{equation}
\mathbf{\hat{\alpha}} = \mathbf{\hat{y}}(\mathbf{\hat{k}^{xx}}+\lambda)^{-1}
\label{eq:FourierDualDomainSolution}
\end{equation}
where $\lambda$ represents the regularization weight whereas $\mathbf{\hat{k}^{xx}}$ denotes
 the first row of the kernel matrix $\mathbf{K}$ known as \textit{gram matrix} and is expressed as
\begin{equation}
\mathbf{k^{xx^{'}}} = exp(-\dfrac{1}{\alpha^{2}}(||\mathbf{x}||^{2}+||\mathbf{x}^{'}||^{2}-2F^{-1}(\sum^{C}_{c}\mathbf{\hat{x}_{c}}^{*}\odot \mathbf{\hat{x}_{c}}^{'}))).
\label{eq:GaussianCorrelationSingleChannel}
\end{equation}
An early version based on this formulation used grayscale feature
($C=1$) to learn the solution vector $\mathbf{w}$ and integrating
multi-channel features such as HoG and Color showed improved accuracy
\cite{henriques2015high,galoogahi2013multi,tang2015multi,ma2015long,bibi2015multi}.
In the detection phase, the learned correlation filter is correlated
with the first row of the gram matrix, $\mathbf{k^{xz^{'}}}$, which
contains the similarity values between the learned feature template
$\mathbf{x}$ and the new test template $\mathbf{z}$. This can be
formulated as
\begin{equation}
\mathbf{r(z)} = F^{-1}(\mathbf{\hat{k}^{xz}} \odot \mathbf{\hat{\alpha}})
\end{equation}
where $\mathbf{r}$ denotes the correlation response at all cyclic shifts of the
first row of the kernel matrix.

@@

%----------------------------------------------------------------------
\section{Experiments} \label{sc:Experiments}
%----------------------------------------------------------------------
So far we explained how the proposed algorithm could efficiently
perform a single-target tracking task while effectively addressing
variations in scale and translation of moving objects. To accurately
evaluate the performance of the proposed algorithm in terms of the
goal of this paper, we need data with challenging variations in scale
and translation. To this end, we chose the UAV123
data\footnote{\url{https://ivul.kaust.edu.sa/Pages/Dataset-UAV123.aspx}}\cite{mueller2016uav123}
that contains 123 video sequences of moving objects captured from
low-altitude UAVs. Because of the nature of the video acquisition --
the targets and the camera are moving together, this data pose a great
deal of challenges as the scale and position of the targets can be
drastically changed in a few frames. To verify that our algorithm is
useful not only for the image data with such extreme challenges but
also for the one with nominal difficulties in single-object tracking,
we also used the OTB100
data\footnote{\url{http://cvlab.hanyang.ac.kr/tracker_benchmark/benchmark_v10.html}}
that contains the videos recorded from smart phones and typical
cameras in perspective view. In addition, we temporarily down-sampled
the UAV123 data to check how robust our algorithm is to drastic
motions of camera and moving targets. Lastly, we evaluate the proposed
algorithm with deep convolutional features, on the UAV123 dataset to
investigate how much performance gain we can achieve in using deep
features over the conventional features like fHoG and color-naming.

@@

\textbf{Performance on UAV123 Dataset} We used the precision and
success rates to compare the performance of the proposed algorithm
with those of the state-of-the-art tracking algorithms. For the
precision, we rank the trackers based on the precision numbers at 20
pixels whereas in the success rate plots, they are ranked based on the
area under curve (AUC) scores. The tracking algorithms under the
comparison include ones in high-speed ($\geq$300 fps): KCF
\cite{henriques2015high}, CSK \cite{henriques2012exploiting}, DCF
\cite{henriques2015high}, MOSSE \cite{bolme2010visual}, and STC
\cite{zhang2014fast} and ones in relatively lower-speed ($\leq$50):
ECO \cite{DanelljanCVPR2017}, CCOT \cite{DanelljanECCV2016}, SCT
\cite{Choi_2016_CVPR}, SAMF \cite{li2014scale}, DSST
\cite{danelljan2014accurate}, Struck \cite{hare2012efficient}, MUSTER
\cite{hong2015multi}, TLD \cite{kalal2012tracking}, and OAB
\cite{zhang2012robust}. The ECO and CCOT trackers originally uses deep
convolutional features, however, to perform fair comparison, we employ
fHoG and color-naming features similar to our tracker. Figure
\ref{fig:UAV123_DATASET} shows the results on the UAV123 dataset. The
    {\it E}nKCF outperformed other high-speed trackers by $3\%$-$15\%$
    at 20 pixels precision. In particular, three algorithms, SAMF,
    DSST, and Struck did about $5\%$ better than ours in accuracy, but
    10-20 times slower. The more recent trackers, ECO and CCOT, on the
    other hand, outperforms {\it E}nKCF by $15\%$ while running at
    10-15 times slower. For the scale adaptation, {\it E}nKCF did
    fourth best in terms of AUC for the success rate plot. It
    outperformed other high-speed trackers by about $20\%$-$25\%$ in
    AUC. In addition, it performed even better than some of the
    lower-speed trackers.  For example, for AUC, {\it E}nKCF
    outperformed Struck and DSST by $5\%$ and $10\%$ while running at
    more than $10$ and $30$ times faster. For the DSST, we believe our
    algorithm outperformed it because, first of all, the DSST uses a
    1-D scale filter and searches the target's scale over 33
    candidates in a scale pool whereas our algorithm uses a 2-D scale
    filter with 3 candidate scales. Learning a 2-D filter would result
    in learning more spatial information. Second of all, the DSST use
    only fHoG whereas our algorithm uses both fHoG and color-naming
    features. Learning more features, not for always, but would
    provide better understanding on the ROI.

@@

\textbf{Evaluation on Particle Filter Contribution} For the UAV123
dataset, we also evaluated the performance of the {\it E}nKCF with and
without the particle filter. In particular, we use 50 video sequences
with no drastic camera motion. To evaluate the robustness of particle
filter, we add noise from a uniform distribution ($[-20,20]$), to the
translation estimations of the KCFs. For this experiment, the {\it
  E}nKCF with particle filter achieves $51.98\%$ precision ($20$px),
outperforming the one without particle filter {\it E}nKCF by
$6.32\%$. This experiment validated that the integration of particle
filter into the {\it E}nKCF can further improve the performance.

@@

\textbf{Performance on UAV123$\_$10fps Dataset} We were curious about
how the frame rate of a testing video would affect the performance of
a tracking algorithm. To this end, we use the temporarily down-sampled
version of the UAV123, called UAV123$\_$10fps dataset. We believe the
downsampling would make the original UAV123 data more challenging
because the displacements of the moving objects become even bigger. To
tackle this challenge, we slightly modified the proposed algorithm --
ran $R_{t}^{L}$ every frame and removed the particle filter due to
larger ego-motion. Figure \ref{fig:UAV123_10fpsDATASET} shows the
performance of the modified version of {\it E}nKCF and other tracking
methods. The precision rates of the ECO and CCOT dropped about $10\%$
in comparison to the original UAV123 dataset. Our tracker outperforms
other high-speed correlation filter based trackers including KCF, DSST
by about $15\%$-$20\%$ and showed a precision rate similar to that of
SAMF. It ranks as fourth in AUC while running about $10$ to $100$
times faster than the top three trackers. It was interesting to
observe how sensitive the performance of the state-of-the-art tracking
algorithms is the frame rate, and, with a slight modification, the
proposed method effectively handled large displacement of objects in
successive frames.
\begin{comment}
\textit{YoungWoo : I also believe that we should
  emphasize how the state-of-the-art trackers perform in lower frame
  rates. And I believe this is what this paper
  \cite{mueller2017context} says. They rank the trackers by evaluating
  them on videos matching their fps. I was thinking of running ECO and
  CCOT in UAV123 in 5 fps videos and mention how they degrade with
  respect to the decreasing fps.  I believe this is our contribution
  and we should emphasize it.

  Burak: To be honest with you, it's a cheating -- we modified our
  algorithm to make it work better, but didn't do anything or
  modifications to other algorithms. Yes, all other algorithms didn't
  perform well on a low frame rate, but it was a unfair comparison. So
  I wouldn't think it's a contribution.  }
\end{comment}
\begin{figure}[!h]
\centering
\begin{tabular}{cc}
\tiny\quad\textbf{UAV123$\_$10fps}\\
\includegraphics[width=3.32cm]{./figures/pr_uav123_10fps.eps}
\includegraphics[width=3.30cm]{./figures/sr_uav123_10fps.eps}\\
\end{tabular}
\caption{Comparison of a modified {\it E}nKCF's performance with those
  of the state-of-the-art tracking algorithms on a lower frame rate
  data.}
\label{fig:UAV123_10fpsDATASET}
\end{figure}

>>>>

The KCF solves essentially the problem of a regression in the form of
the regularization (ridge regression):
\begin{equation}
E(h) = \frac{1}{2}||\mathbf{y}-\sum_{c=1}^{C}\mathbf{h_{c}}*\mathbf{x_{c}}||^{2} + \frac{\lambda}{2}\sum_{c=1}^{C}||\mathbf{h_{c}}||^{2}
\label{eq:Closedform_RidgeReg}
\end{equation}
where we seek for $\mathbf{h}$ that minimizes $E$ given the desired
continuous response, $\mathbf{y}$, and the training template
$\mathbf{x}$.  The parameter $c$ enables one to integrate features in
the form of multiple channels, such as HoG and color, in this setup
\cite{henriques2015high,galoogahi2013multi}.  A closed-form solution
for Equation \ref{eq:Closedform_RidgeReg} exists. To simplify the
closed-form solution, an element-wise multiplication in frequency
domain was proposed to learn the frequency domain correspondence of
$\mathbf{h}$, $\mathbf{\hat{w}}$:
\begin{equation}
\mathbf{\hat{w}} = \mathbf{\hat{x}^{*}}*\mathbf{\hat{y}}(\mathbf{\hat{x}^{*}}*\mathbf{\hat{x}}+\lambda)^{-1}.
\label{eq:DiagonalizedPrimalSolution}
\end{equation}
A non-linear version of $\mathbf{\hat{w}}$, $\mathbf{\hat{\alpha}}$ , is proposed to increase robustness
to any geometric and photometric variations
\cite{henriques2015high}. In particular, the diagonalized non-linear Fourier
domain dual form solution is expressed as
\begin{equation}
\mathbf{\hat{\alpha}} = \mathbf{\hat{y}}(\mathbf{\hat{k}^{xx}}+\lambda)^{-1}
\label{eq:FourierDualDomainSolution}
\end{equation}
where $\lambda$ represents the regularization weight whereas $\mathbf{\hat{k}^{xx}}$ denotes
 the first row of the kernel matrix $\mathbf{K}$ known as \textit{gram matrix} and is expressed as
\begin{equation}
\mathbf{k^{xx^{'}}} = exp(-\dfrac{1}{\alpha^{2}}(||\mathbf{x}||^{2}+||\mathbf{x}^{'}||^{2}-2F^{-1}(\sum^{C}_{c}\mathbf{\hat{x}_{c}}^{*}\odot \mathbf{\hat{x}_{c}}^{'}))).
\label{eq:GaussianCorrelationSingleChannel}
\end{equation}
An early version based on this formulation used grayscale feature
($C=1$) to learn the solution vector $\mathbf{w}$ and integrating
multi-channel features such as HoG and Color showed improved accuracy
\cite{henriques2015high,galoogahi2013multi,tang2015multi,ma2015long,bibi2015multi}.
In the detection phase, the learned correlation filter is correlated
with the first row of the gram matrix, $\mathbf{k^{xz^{'}}}$, which
contains the similarity values between the learned feature template
$\mathbf{x}$ and the new test template $\mathbf{z}$. This can be
formulated as
\begin{equation}
\mathbf{r(z)} = F^{-1}(\mathbf{\hat{k}^{xz}} \odot \mathbf{\hat{\alpha}})
\end{equation}
where $\mathbf{r}$ denotes the correlation response at all cyclic shifts of the
first row of the kernel matrix.
\begin{comment}
As a common practice, to integrate further temporal information into tracker, we
update the correlation filter and the appearance model as below.
\begin{align}
\mathbf{\hat{\alpha}_{t}} = (1-\beta) \mathbf{\hat{\alpha}_{t-1}} + \beta \mathbf{\hat{\alpha}_{t}} \\
\mathbf{x_{t}} = (1-\beta) \mathbf{x_{t-1}} + \beta \mathbf{x_{t}}.
\end{align}
\end{comment}

@@

%----------------------------------------------------------------------
\section{Experiments} \label{sc:Experiments}
%----------------------------------------------------------------------
So far we explained how the proposed algorithm could efficiently
perform a single-target tracking task while effectively addressing
variations in scale and translation of moving objects. To accurately
evaluate the performance of the proposed algorithm in terms of the
goal of this paper, we need data with challenging variations in scale
and translation. To this end, we chose the UAV123
data\footnote{\url{https://ivul.kaust.edu.sa/Pages/Dataset-UAV123.aspx}}\cite{mueller2016uav123}
that contains 123 video sequences of moving objects captured from
low-altitude UAVs. Because of the nature of the video acquisition --
the targets and the camera are moving together, this data pose a great
deal of challenges as the scale and position of the targets can be
drastically changed in a few frames. To verify that our algorithm is
useful not only for the image data with such extreme challenges but
also for the one with nominal difficulties in single-object tracking,
we also used the OTB100
data\footnote{\url{http://cvlab.hanyang.ac.kr/tracker_benchmark/benchmark_v10.html}}
that contains the videos recorded from smart phones and typical
cameras in perspective view. In addition, we use a temporarily
down-sampled the UAV123 data to check how robust our algorithm is to
drastic motions of camera and moving targets. Lastly, we evaluate the
proposed algorithm with deep convolutional features on the UAV123
dataset to investigate how much performance gain we can achieve in
using deep features over the conventional features like fHoG and
color-naming.

@@

\textbf{Performance on UAV123 Dataset} We used the precision and
success rates to compare the performance of the proposed algorithm
with those of the state-of-the-art tracking algorithms. For the
precision, we rank the trackers based on the precision numbers at 20
pixels whereas in the success rate plots, they are ranked based on the
area under curve (AUC) scores. The tracking algorithms under the
comparison include ones in high-speed ($\geq$300 fps): KCF
\cite{henriques2015high}, CSK \cite{henriques2012exploiting}, DCF
\cite{henriques2015high}, MOSSE \cite{bolme2010visual}, and STC
\cite{zhang2014fast} and ones in relatively lower-speed ($\leq$50):
ECO \cite{DanelljanCVPR2017}, CCOT \cite{DanelljanECCV2016}, SCT
\cite{Choi_2016_CVPR}, SAMF \cite{li2014scale}, DSST
\cite{danelljan2014accurate}, Struck \cite{hare2012efficient}, MUSTER
\cite{hong2015multi}, TLD \cite{kalal2012tracking}, and OAB
\cite{zhang2012robust}. The ECO and CCOT trackers originally uses deep
convolutional features, however, to perform fair comparison, we employ
fHoG and color-naming features similar to our tracker. Figure
\ref{fig:UAV123_DATASET} shows the results on the UAV123 dataset. The
    {\it E}nKCF outperformed other high-speed trackers by $3\%$-$15\%$
    at 20 pixels precision. In particular, three algorithms, SAMF,
    DSST, and Struck did about $5\%$ better than ours in accuracy, but
    10-20 times slower. The more recent trackers, ECO and CCOT, on the
    other hand, outperforms {\it E}nKCF by $15\%$ while running at
    10-15 times slower. For the scale adaptation, {\it E}nKCF did
    fourth best in terms of AUC for the success rate plot. It
    outperformed other high-speed trackers by about $20\%$-$25\%$ in
    AUC. In addition, it performed even better than some of the
    lower-speed trackers.  For example, for AUC, {\it E}nKCF
    outperformed Struck and DSST by $5\%$ and $10\%$ while running at
    more than $10$ and $30$ times faster. For the DSST, we believe our
    algorithm outperformed it because, first of all, the DSST uses a
    1-D scale filter and searches the target's scale over 33
    candidates in a scale pool whereas our algorithm uses a 2-D scale
    filter with 3 candidate scales. Learning a 2-D filter resulted in
    learning more spatial information. Second of all, the DSST use
    only fHoG whereas our algorithm uses both fHoG and color-naming
    features. Learning more features, not always, but provided a
    better understanding on the ROI.

@@

\textbf{Evaluation on Particle Filter Contribution} For the UAV123
dataset, we also evaluated the performance of the {\it E}nKCF with and
without the particle filter. In particular, we use 50 video sequences
with no drastic camera motion. To evaluate the robustness of particle
filter, we add noise from a uniform distribution ($[-20,20]$), to the
translation estimations of the KCFs. For this experiment, the {\it
  E}nKCF with particle filter achieves $51.98\%$ precision ($20$px),
outperforming the one without particle filter by $6.32\%$. This
experiment validated that the integration of particle filter into the
{\it E}nKCF can further improve the performance.

@@

\textbf{Performance on UAV123$\_$10fps Dataset} We were curious about
how the frame rate of a testing video would affect the performance of
a tracking algorithm. To this end, we use the temporarily down-sampled
version of the UAV123, called UAV123$\_$10fps dataset. We believe the
downsampling would make the original UAV123 data more challenging
because the displacements of the moving objects become even bigger. To
tackle this challenge, we slightly modified the proposed algorithm --
ran $R_{t}^{L}$ every frame and removed the particle filter due to
larger ego-motion. Figure \ref{fig:UAV123_10fpsDATASET} shows the
performance of the modified version of {\it E}nKCF and other tracking
methods. The precision rates of the ECO and CCOT dropped about $10\%$
in comparison to the original UAV123 dataset. Our tracker outperforms
other high-speed correlation filter based trackers including KCF, DSST
by about $15\%$-$20\%$ and showed a precision rate similar to that of
SAMF. It ranks as fourth in AUC while running about $10$ to $100$
times faster than the top three trackers. It was interesting to
observe how sensitive the performance of the state-of-the-art tracking
algorithms is to the frame rate, and, with a slight modification, the
proposed method effectively handled large displacement of objects in
successive frames.

\begin{figure}[!h]
\centering
\begin{tabular}{cc}
\tiny\quad\textbf{UAV123$\_$10fps}\\
\includegraphics[width=3.32cm]{./figures/pr_uav123_10fps.eps}
\includegraphics[width=3.30cm]{./figures/sr_uav123_10fps.eps}\\
\end{tabular}
\caption{Comparison of a modified {\it E}nKCF's performance with those
  of the state-of-the-art tracking algorithms on a lower frame rate
  data.}
\label{fig:UAV123_10fpsDATASET}
\end{figure}
